Using Fundamental Measure Theory to Treat the Correlation Function of the Inhomogeneous Hard-Sphere Fluid

### 2012-08-29 papers/contact/paper.tex
a few more edits to contact paper Tested everything on darcy.

The $g_\sigma^A$ correlation function in each configuration is very
flat, with only small, smooth changes as the surface is approached.
Our functional $g_\sigma^A$ very closely matches the Monte Carlo
predictions in each case, while that of Gross consistently
underestimates the correlation at the interface by
\textcolor{red}{several percent}.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/outer-16-01}
  \caption{Density and contact densities at a xxx with bulk filling
    fraction of 0.1.}
  \label{fig:outer-10}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/outer-16-04}
  \caption{Density and contact densities at a xxx with bulk filling
    fraction of 0.4.}
  \label{fig:outer-40}
\end{figure}

>>>>

The $g_\sigma^A$ correlation function in each configuration is very
flat, with only small, smooth changes as the surface is approached.
Our functional $g_\sigma^A$ very closely matches the Monte Carlo
predictions in each case, while that of Gross consistently
underestimates the correlation at the interface by
\textcolor{red}{several percent}.  We note that the theoretical curves
extend into the region from which the fluid is excluded.  This value
corresponds to the correlation function that would be observed in the
vanishingly unlikely scenario in which there was a sphere present at
that location.  Naturally, we are unable to observe this quantity in
our Monte Carlo simulations.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/outer-16-01}
  \caption{Density and correlation functions near the surface of a
    spherical cavity with diameter $16\sigma$ at a bulk filling
    fraction of 0.1.}
  \label{fig:outer-10}
\end{figure}

@@

At a higher density corresponding to a filling fraction of 0.4,
correlations are much stronger, with the bulk contact value of the
correlation function of 3.7, as seen in
Figures~\ref{fig:walls-40}-\ref{fig:outer-40}.  This results in larger
oscillations in the density at the hard surfaces, and correspondingly
more interesting behavior in the correlation function near the
interface.  The density predicted by the White Bear functional agrees
reasonably well with the simulation results, although not so well as
it did at lower density.  The discrepancies are largest in the case of
the spherical cavity, in which the DFT considerably underestimates the
range of the density oscillations.

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/outer-16-04}
  \caption{Density and correlation functions near the surface of a
    spherical cavity with diameter $16\sigma$ at a bulk filling
    fraction of 0.4.}
  \label{fig:outer-40}
\end{figure}

The asymmetric version of the correlation function once again displays
relatively smooth behavior near the interface, with a few small
oscillations near the interface, and a somewhat elevated value within
a diameter of the hard surface, with the magnitude of this elevation
somewhat different in each configuration.  As was the case at low
density, our correlation function $g_\sigma^A$ matches very closely
the Monte Carlo data, reproducing quite well the structure near the
interface in each configuration, although in the spherical cavity
(Figure~\ref{fig:outer-40}), there is a small, but significant
discrepancy, comparable to the discrepancy found in the density
itself.  In each case, the correlation of Gross dramatically
underestimates the correlation at the interface, at one extreme by
\fixme{40\%} in the case of the spherical cavity
(Figure~\ref{fig:outer-40}), and at the other extreme by \fixme{10\%}
in the test-particle scenario (Figure~\ref{fig:inner-4-40}).

The symmetrically averaged correlation function shows considerably
more structure near the interface at high density, and this structure
varies considerably depending on the curvature of the hard surface.
In each case, this structure is not reflected in the theoretical
predictions, neither that of this paper, nor that of Yu and
Wu~\cite{yu2002fmt-dft-inhomogeneous-associating}.  As was the case at
low density, both functionals give significant and finite values in
the region in which there are no contacts, but at high density they
also miss the large oscillations that are present near the flat wall
and the concave surface (Figures~\ref{fig:walls-40}
and~\ref{fig:outer-40}).  As was the case at low density, the
functional of Yu and Wu~\cite{yu2002fmt-dft-inhomogeneous-associating}
gives slightly better agreement with the simulation results than that
which we derive in Section~\ref{sec:g-S}.
